Topological Equivariant Artist Model

### 2022-01-27 slides/main.tex
equivariance
defining output/delta
complex data

                \item[\textcolor{base}{Continuity \gbasec}]{parameterization of the graphic's geometry}

@@

    \frametitle<3|handout:3>{Functor: $\vindexc: \opensetgc \rightarrow \opensetc$}

@@

\section{Equivariant Artist}

\begin{frame}{Bundle Map \dfuncc?}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}

    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}{$\dfuncc = (\dfunchc, \dfuncpullc, \dfunctc)$}
    \begin{tikzcd}[ampersand replacement = \&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rr, "\dfuncpullc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[rr, "\dfunctc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \\
        \&  \&  
        \&  \& \\
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \dtotalc}}", maps to, color=sheaf]                 
        \&  \& 
        \opensetc^{\prime} 
        \arrow[ll, "\dfunchc", color=action] 
        \arrow[uu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \arrow[rruu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \&  \& 
    \end{tikzcd}
    \begin{itemize}
        \item Base $\dbasec$ Type stays same: $\dfunchc: \dbasec \rightarrow \dbasec$
        \item Fiber $\dfiberc$ Type stays the same: $\dfunctc: \dfuncpullc \dtotalc \rightarrow \dfuncpullc\dtotalc$ s.t. $\pi(\dfuncpullc\dtotalc) = \pi(\dfunctc(\dfuncpullc\dtotalc))$ 
        \item Section Transform: $\dfuncc: \dsectionc^{a}\restriction_{\opensetc} \mapsto \dsectionc^{b}\restriction_{\opensetc^{\prime}}$
    \end{itemize}
\end{frame}

\begin{frame}{Continuity Equivariance: $\dfunchc_{\dbasec}\circ \vindexc = \vindexc \circ \dfunchc_{\gbasec}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \opensetgc 
        \arrow[rr, "\vindexc", color=functor] 
        \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
        \&  \& 
        \opensetc 
        \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
        \&  \& \\
        \opensetgc^{\prime} 
        \arrow[rr, "\vindexc"', color=functor]
        \&  \& 
        \opensetc^{\prime}\\
        \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
        \end{tikzcd}
    \end{equation*}

@@

\begin{frame}{Field Equivariance: $\vartist \circ (\dfunctc_{\dtotalc}\circ \dfuncpullc_{\dbasec}) =  (\dfunctc_{\gtotalc} \circ \dfuncpullc_{\gbasec}) \circ \vartist$}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dbasec}\dtotalc\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", color=artist, Rightarrow] 
            \arrow[dd, "\dfunctc_{\dtotalc}\circ \dfuncpullc_{\dbasec}"', color=action] 
            \&  \& 
            \vartistc[\dfuncpullc\sheafc_{\dbasec,\dtotalc}] \subset \cgamma{\opensetgc^{\prime}}{\dfuncpullc_{\gbasec}\gtotalc\restriction_{\opensetgc^{\prime}}} 
            \arrow[dd, "\dfunctc_{\gtotalc}\circ \dfuncpullc_{\gbasec}", dashed, color=action, shift right=5em] \\
            \&  \&
            \\
            \cgamma{\opensetc^{\prime}}{\dfunctc_{\dtotalc}\dfuncpullc_{\dbasec}\dtotalc\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", color=artist, Rightarrow]
            \&  \& 
            \vartistc[\dfunctc\dfuncpullc\sheafc_{\dbasec,\dtotalc}] \subset \cgamma{\opensetgc^{\prime}}{\dfunctc_{\gtotalc}\dfuncpullc_{\gbasec}\gtotalc\restriction_{\opensetgc^{\prime}}}                                                  
    \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \sheafc_{\dbasec, \dtotalc} 
        \arrow[r, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncc_{\dsectionc}"', color=action] \& 
        \sheafc_{\vartistc} 
        \arrow[d, "\dfuncc_{\gsectionc}", color=action, dashed] \\
        \dfuncc_{\dsectionc}\sheafc_{\dbasec, \dtotalc} 
        \arrow[r, "\vartistc", Rightarrow, color=artist]    \& 
        \dfuncc_{\gsectionc}\sheafc_{\vartistc}    
        \end{tikzcd} 
    \end{equation*}

    \begin{proposition}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dsectionc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dsectionc}(\dsectionc^{b})) \
        \end{align*}
    \end{proposition}
\end{frame}

\begin{frame}{Multiple Fields: $\dfuncc = (\dfunchc, \dfuncpullc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \circ \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i \circ \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \circ \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \circ \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]}) \circ \dbasec }                                             \& \& = \& 
                \dfunchc \circ \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

    \begin{block}{Add New Field to E}
        \begin{description}[style=newline]
            \item[construct] {$\odot:\dfiberc_{field} \times \dbasec \rightarrow \dtotalc_{field}$}
            \item[concatenate]{$\otimes: \dtotalc_{field} \times \dtotalc \mapsto \dtotalc$ s.t. $\pi(\dtotalc_{field}) = \pi(\dtotalc)$}
        \end{description}
    \end{block}

\begin{frame}{Field Equivariance}

    \begin{equation*}
        \oslash: \vartistc \times \dfiberc \rightarrow visual\; encoding
    \end{equation*}

\begin{equation*}
    \begin{tikzcd}[ampersand replacement = \&]
            \& 
            {\sheafc_{\dbasec, \dtotalc}}
            \arrow[rr, "\vartistc"]                   
            \&  \& 
            \sheafc_{\vartist} 
            \arrow[rd, "\oslash_{\dfiber_{field}}"]           \&                        \\
            \dfiberc_{field} 
            \arrow[ru, "\otimes_{\dtotalc} \circ \odot_{\dbasec}"] 
            \arrow[rd, "\otimes_{\dtotalc^{\prime}} \circ \odot_{\dbasec^{\prime}}"'] 
            \& \& \& \& 
            visual\;encoding \\
            \& 
            {\sheafc_{\dbasec^{\prime}, \dtotalc^{\prime}}} 
            \arrow[rr, "\vartistc"'] 
            \& \& 
            \sheafc_{\vartist}^{\prime} 
            \arrow[ru, "\oslash_{\dfiber_{field}}"'] 
            \&                       
    \end{tikzcd}
\end{equation*}

>>>>

                \item[\textcolor{base}{Continuity \gbasec}]{parameterization of graphic area (e.g. "inked" bounding box\cite{CairographicsOrg})}

@@

    \frametitle<3|handout:3>{Function: $\vindexc: \gbasec \rightarrow \dbasec$}

@@

\begin{frame}{Output}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[rrd, "\delta"'] 
            \arrow[rr, "render"] \&  \& visualization 
            \arrow[d, "measure" description] \\ 
            \&  \&  \&  \& M
            \end{tikzcd}
    \end{equation*}
\end{frame}

\section{Equivariant Artist}
\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}{$\dfuncc = (\dfunchc, \dfunctc)$}
    \begin{tikzcd}[ampersand replacement = \&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rr, "\dfuncpullc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[rr, "\dfunctc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \\
        \&  \&  
        \&  \& \\
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \dtotalc}}", maps to, color=sheaf]                 
        \&  \& 
        \opensetc^{\prime} 
        \arrow[ll, "\dfunchc", color=action] 
        \arrow[uu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \arrow[rruu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \&  \& 
    \end{tikzcd}
    \begin{itemize}
        \item Base $\dbasec$ Type stays same: $\dfunchc: \dbasec \rightarrow \dbasec$
        \item Fiber $\dfiberc$ Type stays the same: $\dfunctc: \dfuncpullc \dtotalc \rightarrow \dfuncpullc\dtotalc$ s.t. $\pi(\dfuncpullc\dtotalc) = \pi(\dfunctc(\dfuncpullc\dtotalc))$ 
        \item Section Transform: $\dfuncc: \dsectionc^{a}\restriction_{\opensetc} \mapsto \dsectionc^{b}\restriction_{\opensetc^{\prime}}$
    \end{itemize}
\end{frame}

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \sheafc_{\dbasec, \dtotalc} 
        \arrow[r, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncc_{\dtotalc}"', color=action] \& 
        \sheafc_{\gbasec, \gtotalc} 
        \arrow[d, "\dfuncc_{\gtotalc}", color=action, dashed] \\
        \sheafc_{\dbasec^{\prime}, \dfuncpullc\dtotalc} 
        \arrow[r, "\vartistc", Rightarrow, color=artist]    \& 
        \sheafc_{\gbasec^{\prime},\dfuncpullc{\gbasec}\gtotalc}    
        \end{tikzcd} 
    \end{equation*}

    \begin{proposition}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b})) \
        \end{align*}
    \end{proposition}
\end{frame}

\begin{frame}{Equivariant $\dfunchc$}
    \note{Maybe move to implementation section}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]
            \opensetgc 
            \arrow[rr, "\vindexc", color=functor] 
            \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
            \&  \& 
            \opensetc 
            \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
            \&  \& \\
            \opensetgc^{\prime} 
            \arrow[rr, "\vindexc"', color=functor]
            \&  \& 
            \opensetc^{\prime}\\
            \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
            \end{tikzcd}
        \end{equation*}
\end{frame}

\begin{frame}{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc"', Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] 
            \arrow[rrr, "\equivc", bend left, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[r, "\delta"']\& M 
            \arrow[d, "\dfuncc_{M}", color=action] \\
            \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] 
            \arrow[rrr, "\equivc"', bend right, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc^{\prime}}{\dfuncpullc\gtotalc\restriction_{\opensetgc^{\prime}}} 
            \arrow[r, "\delta"] \& M^{\prime}                        
        \end{tikzcd}
    \end{equation*}
        there exists a monoid homomorphism $\equivc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{M}$ such that 
        \begin{description}
            \item[equivariance] $\equivc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{M}(\equivc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\equivc(\dsectionc(x))) = \equivc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
        \end{description} 
\end{frame}

\section{Complex Structure}
\begin{frame}{Multiple Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \circ \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i \circ \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \circ \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \circ \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]}) \circ \dbasec }                                             \& \& = \& 
                \dfunchc \circ \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

@@

\begin{frame}{complex data}
    \begin{description}[style=newline]
        \item[combining continuities]{given $\dbasepointc_{a} \in \dbasec_{c} \subset \dbasec_{a}$ and $\dbasepointc_{b} \in \dbasec_{c} \subset \dbasec_{b}$, if $\dbasepointc_{a} = \dbasepointc_{b}$ then $\equivc(\dsectionc(\dbasepointc_{a})) = \equivc(\dsectionc(\dbasepointc_{b}))$ for all $\dbasepointc_{a}, \dbasepointc_{b} \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$}
        \item[shared fibers]{
            if $p = p^{\prime}$ then $\equivc \circ q$ = $\equivc^{\prime} \circ q^{\prime}$
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
        \& \dfiberc^a \times \dfiberc^b 
        \arrow[ld, "p"', color=fiber] 
        \arrow[rd, "q \circ \equivc"] \&     \\
        \dfiberc^a \& \& M^a \\
        \& \dfiberc^a \times \dfiberc^c 
        \arrow[lu, "p^{\prime}", color=fiber] 
        \arrow[ru, " q^{\prime} \circ\equivc^{\prime}"'] \&    
      \end{tikzcd}
    \end{equation*}}         
        \item[both]{given $\dsectionc^{a} \in \sheafc_{\dbasec_a, \dtotalc_a}, \dsectionc^{b} \in \sheafc_{\dbasec_b, \dtotalc_b}$ and $\dbasepointc \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$ then $q(\equivc(\dsection^a(\dbasepointc))) = q^{\prime}(\equivc(\dsectionc^b(\dbasepointc)))$ when $p(\dfiberc^{a}\restriction_{\dbasepointc}) = p^{\prime}(\dfiberc^{b}\restriction_{\dbasepointc})$}
    \end{description}
\end{frame}
